### 2021-11-24 README.Rmd
spelling check

The next example uses the `plot_type = "dotplot"` to visualise the distribution of the data, and also customizes the position of the legend using a `ggplot` theme as well.

>>>>

The next example uses the `plot_type = "dotplot"` to visualize the distribution of the data, and also customizes the position of the legend using a `ggplot` theme as well.
